---
title: "p8105_hw6_slb2240"
author: "Samantha Brown"
date: "11/19/2018"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(purrr)
library(broom)
library("leaps")
```

## Problem 1

The Washington Post has gathered data on homicides in 50 large U.S. cities and made the data available through a GitHub repository here.

_Create a city_state variable (e.g. “Baltimore, MD”), and a binary variable indicating whether the homicide is solved. Omit cities Dallas, TX; Phoenix, AZ; and Kansas City, MO – these don’t report victim race. Also omit Tulsa, AL – this is a data entry mistake. Modifiy victim_race to have categories white and non-white, with white as the reference category. Be sure that victim_age is numeric._



```{r, warning = FALSE}
## Read in and wrangle data
homicide_data = read.csv("./homicide-data.csv") %>% 
  mutate(city_state = str_c(city, ", ", state)) %>% 
  filter(!(city_state %in% c("Tulsa, AL", "Dallas, TX", "Phoenix, AZ", "Kansas City, MO"))) %>% 
  mutate(homicide_solved = as.numeric(disposition == "Closed by arrest"),
         victim_race = ifelse(victim_race != "White", "nonwhite", "white"),
         victim_race = fct_relevel(victim_race, ref = "white"),
         victim_age = as.numeric(victim_age))


```



_For the city of Baltimore, MD, use the glm function to fit a logistic regression with resolved vs unresolved as the outcome and victim age, sex and race (as just defined) as predictors. Save the output of glm as an R object; apply the broom::tidy to this object; and obtain the estimate and confidence interval of the adjusted odds ratio for solving  homicides comparing non-white victims to white victims keeping all other variables fixed._



```{r}
## Filter data to look at Baltimore, MD only
baltimore_data = homicide_data %>% 
  filter(city_state == "Baltimore, MD")

## Fit logistic regression
baltimore_glm = baltimore_data %>% 
  glm(homicide_solved ~ victim_age + victim_race + victim_sex, data = ., family = binomial())
  
## Clean up model and obtain odds ratio and CI for odds ratio
baltimore_glm %>% 
  broom::tidy(conf.int = TRUE) %>% 
  mutate(OR = exp(estimate),
         lower_bound = exp(conf.low),
         upper_bound = exp(conf.high)) %>% 
  select(term, OR, lower_bound, upper_bound) %>% 
  filter(term == "victim_racenonwhite") %>% 
  knitr::kable(digits = 3)
```


I am 95% confident that the true odds ratio for homicides comparing non-white victims to white victims is between 0.321 and 0.63, keeping all other variables fixed.


_Now run glm for each of the cities in your dataset, and extract the adjusted odds ratio (and CI) for solving homicides comparing black victims to white victims. Do this within a “tidy” pipeline, making use of purrr::map, list columns, and unnest as necessary to create a dataframe with estimated ORs and CIs for each city._

_Create a plot that shows the estimated ORs and CIs for each city. Organize cities according to estimated OR, and comment on the plot._

```{r, warning = FALSE}
## Extract adjusted odds ratio and confidence intervals for all cities in dataset
homicide_data %>% 
  group_by(city_state) %>% 
  nest() %>% 
  mutate(models = map(data, ~glm(homicide_solved ~ victim_age + victim_sex + victim_race, data = ., family = binomial())),
         CI_models = map(models, broom::confint_tidy)) %>% 
  mutate(models = map(models, broom::tidy)) %>% 
  select(-data) %>%
  unnest() %>% 
  filter(term == "victim_racenonwhite") %>% 
  mutate(OR = exp(estimate),
         lower_bound = exp(conf.low),
         upper_bound = exp(conf.high)) %>% 
  select(city_state, OR, lower_bound, upper_bound) %>% 
  ## Plot OR and confidence intervals
  ggplot(aes(x = reorder(city_state, OR), y = OR)) +
  geom_point() +
  geom_errorbar(aes(ymin = lower_bound, ymax = upper_bound)) +
  coord_flip() +
  labs(
    x = "City, State",
    y = "Odds Ratio and Confidence Interval",
    title = "Odds Ratio and Confidence Interval for Each City",
    caption = "Data source: https://github.com/washingtonpost/data-homicides"
  ) +
  theme(axis.text = element_text(size = 8, hjust = 1))
  
```

## Finish commenting

In the plot above, I calculated the odds ratio and confidence intervals for each city in the dataset. This odds ratio meausres the strength of the assiciation for homicides comparing nonwhite victims to white victims. The plot indicates Boston, MA had the lowest odds ratio, while Tampa, FL had the highest odds ratio.

## Problem 2

_Load and clean the data for regression analysis_ 

```{r}
birthweight_data = read.csv("./birthweight.csv") %>% 
  janitor::clean_names() %>% 
  mutate(babysex = as.factor(ifelse(babysex == 1, "male", "female")),
         frace = as.factor(frace),
         frace = recode_factor(frace, "1" = "white", "2" = "black", "3" = "asian", "4" = "puerto rican", "8" = "other", "9" = "unknown"),
         malform = as.logical(malform),
         mrace = as.factor(mrace),
         mrace = recode_factor(mrace, "1" = "white", "2" = "black", "3" = "asian", "4" = "puerto rican", "8" = "other"))
```



```{r, include = FALSE}
## Check data classes
class(birthweight_data$babysex)
class(birthweight_data$bhead)
class(birthweight_data$blength)
class(birthweight_data$bwt)
class(birthweight_data$delwt)
class(birthweight_data$gaweeks)
class(birthweight_data$fincome)
class(birthweight_data$frace)
class(birthweight_data$malform)
class(birthweight_data$menarche)
class(birthweight_data$mheight)
class(birthweight_data$momage)
class(birthweight_data$mrace)
class(birthweight_data$parity)
class(birthweight_data$pnumlbw)
class(birthweight_data$pnumsga)
class(birthweight_data$ppbmi)
class(birthweight_data$ppwt)
class(birthweight_data$smoken)
class(birthweight_data$wtgain)
```

_Propose a regression model for birthweight. This model may be based on a hypothesized structure for the factors that underly birthweight, on a data-driven model-building process, or a combination of the two. Describe your modeling process and show a plot of model residuals against fitted values – use add_predictions and add_residuals in making this plot._


```{r}
## First, fit a regression using all predictors
mult.fit = lm(bwt ~ ., data = birthweight_data)
summary(mult.fit)

## Stepwise elimination (from Methods I, lecture 18)
step(mult.fit, direction = "backward")
```

I performed a stepwise regression on the `birthweight_data`. I used the `step` function to develop several regression models by adding and eliminating different predictors one at a time, and ultimately identifying the best model. My model includes `babysex`, `bhead`, `blength`, `delwt`, `fincome`, `gaweeks`, `mheight`, `mrace`, `parity`, `ppwt`, and `smoken` as signficant predictors of the baby's weight. My model is summarized in the code chunk below:

```{r}
stepwise_reg = lm(bwt ~ babysex + bhead + blength + delwt + fincome + gaweeks + mheight + mrace + parity + ppwt + smoken, data = birthweight_data)

stepwise_reg %>%
  summary() %>% 
  broom::tidy() %>% 
  knitr::kable(digits = 4)
```

```{r}
## Use modelr package for add_predictions() and add_residuals()
library(modelr)
predictors_and_residuals = birthweight_data %>% 
  add_predictions(stepwise_reg) %>% 
  add_residuals(stepwise_reg)

ggplot(predictors_and_residuals, aes(x = pred, y = resid)) +
  geom_point(alpha = .5, col = "blue") + 
  labs(
    x = "Predicted Value",
    y = "Residual Value",
    title = "Predicted vs. Residual values for stepwise_reg"
  )
```


Compare your model to two others:

* One using length at birth and gestational age as predictors (main effects only)
* One using head circumference, length, sex, and all interactions (including the three-way interaction) between these

```{r}

```


Make this comparison in terms of the cross-validated prediction error; use crossv_mc and functions in purrr as appropriate