---
title: "p8105_hw6_slb2240"
author: "Samantha Brown"
date: "11/19/2018"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(purrr)
```

## Problem 1

The Washington Post has gathered data on homicides in 50 large U.S. cities and made the data available through a GitHub repository here.

_Create a city_state variable (e.g. “Baltimore, MD”), and a binary variable indicating whether the homicide is solved. Omit cities Dallas, TX; Phoenix, AZ; and Kansas City, MO – these don’t report victim race. Also omit Tulsa, AL – this is a data entry mistake. Modifiy victim_race to have categories white and non-white, with white as the reference category. Be sure that victim_age is numeric._



```{r, warning = FALSE}
## Read in and wrangle data
homicide_data = read.csv("./homicide-data.csv") %>% 
  mutate(city_state = str_c(city, ", ", state)) %>% 
  filter(city_state != c("Tulsa, AL", "Dallas, TX", "Phoenix, AZ", "Kansas City, MO")) %>% 
  mutate(homicide_solved = as.numeric(disposition == "Closed by arrest"),
         victim_race = ifelse(victim_race == "White", 1, 0),
         victim_age = as.numeric(victim_age))
```



_For the city of Baltimore, MD, use the glm function to fit a logistic regression with resolved vs unresolved as the outcome and victim age, sex and race (as just defined) as predictors. Save the output of glm as an R object; apply the broom::tidy to this object; and obtain the estimate and confidence interval of the adjusted odds ratio for solving homicides comparing black victims to white victims keeping all other variables fixed._



```{r}
## Filter data to look at Baltimore, MD only
baltimore_data = homicide_data %>% 
  filter(city_state == "Baltimore, MD")

## Fit logistic regression
baltimore_glm = baltimore_data %>% 
  glm(homicide_solved ~ victim_age + victim_race + victim_sex, data = ., family = binomial()) %>% 
  broom::tidy() %>% 
  mutate(OR = exp(estimate),
         OR_upper_bound = exp(estimate) + 1.96*std.error,
         OR_lower_bound = exp(estimate) - 1.96*std.error)

## Obtain estimate and confidence interval
## For the confidence interval, do I need to do exp(1.96*std.error)? Or without exp()? Not sure if this is right
baltimore_glm %>% 
  filter(term == "victim_race") %>% 
  select(term, OR, OR_lower_bound, OR_upper_bound) %>% 
  knitr::kable(digits = 3)
```


I am 95% confident that the true odds ratio for homicides compating non-white victims to white victims is between 1.868 and 2.551, keeping all other variables fixed.


_Now run glm for each of the cities in your dataset, and extract the adjusted odds ratio (and CI) for solving homicides comparing black victims to white victims. Do this within a “tidy” pipeline, making use of purrr::map, list columns, and unnest as necessary to create a dataframe with estimated ORs and CIs for each city._


```{r}
all_cities_nest_glm = homicide_data %>% 
  group_by(city_state) %>% 
  nest() 
  ##mutate(models = map(data, ~glm(homicide_solved ~ victim_age + victim_race + victim_sex, data = .x, family = binomial())),
         ##models = map(models, broom::tidy)) %>% 
  ##select(-data) %>%
  ##unnest()
  
```


_Create a plot that shows the estimated ORs and CIs for each city. Organize cities according to estimated OR, and comment on the plot._







## Problem 2

```{r}
birthweight_data = read.csv("./birthweight.csv") %>% 
  janitor::clean_names() %>% 
  mutate(babysex = as.factor(babysex),
         frace = as.factor(frace),
         malform = as.logical(malform),
         mrace = as.factor(mrace)) %>% 
  select(-pnumlbw, -pnumsga)
```



```{r, include = FALSE}
class(birthweight_data$babysex)
class(birthweight_data$bhead)
class(birthweight_data$blength)
class(birthweight_data$bwt)
class(birthweight_data$delwt)
class(birthweight_data$gaweeks)
class(birthweight_data$fincome)
class(birthweight_data$frace)
class(birthweight_data$malform)
class(birthweight_data$menarche)
class(birthweight_data$mheight)
class(birthweight_data$momage)
class(birthweight_data$mrace)
class(birthweight_data$parity)
class(birthweight_data$pnumlbw)
class(birthweight_data$pnumsga)
class(birthweight_data$ppbmi)
class(birthweight_data$ppwt)
class(birthweight_data$smoken)
class(birthweight_data$wtgain)
```

